---
title: "Perception Action Analysis"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/emmaolsen/PERC-ACT_EXAM")
pacman::p_load(tidyverse,dplyr, data.table, vroom, ggplot2, readbulk, lme4, rstanarm, MuMIn, lmerTest, lme4,multcomp, interactions, sjPlot, sjmisc)

```

Read data
```{r}

df <- read_bulk(directory = "/Users/emmaolsen/PERC-ACT_EXAM/logfiles",
    fun = read_csv)

#df <- read_csv("/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/logfiles_emma/logfile_test_2021_Dec_13_0937_1.csv")
```

Split dataframe
```{r}
# Only colourrating
colourrating <- df[which(df$...1==60),]

# df without 
df_withoutcolour <- df[is.na(df$Colourrating),]
df_withoutcolour$Colourrating <- NULL
df <- df_withoutcolour

```

Remove the weird [' '] part of the Colourtask (key press), leaving only the letter
```{r}
df$Colourtask = gsub("'", "", df$Colourtask)
df$Colourtask = gsub("\\[|\\]", "", df$Colourtask)
unique(df$Colourtask)
```

```{r}
df <- df %>% 
  rename(keypress = Colourtask)
```

Making stimulus variable neat (only leaving y1a format)
```{r}

df$Stimulus = gsub("/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/stimuli/", "", df$Stimulus)
df$Stimulus = gsub("/Users/laura/Desktop/GitHu PercAct/stimuli/", "", df$Stimulus)
df$Stimulus = gsub(".png", "", df$Stimulus)

```

Make a simple stim variable
```{r}

# df$Stimulus = gsub("a", "", df$Stimulus)
df$Stimulus = gsub("b", "", df$Stimulus)
df$Stimulus = gsub("1234567890", "", df$Stimulus)
length(unique(df$Stimulus))
```

Do a subset test
```{r}
#test <- df %>%
 #   filter(ID == "sjovtparticipantid")
```


Create correct variable. If variable 'Stimulus' contains character value y, the variable "correct" should be 
```{r}

df$stimcolour <- substr(df$Stimulus,1,1) #just getting the y/r letter out 
df$correct = ifelse((df$stimcolour=="y" & df$keypress == "y") | (df$stimcolour=="r" & df$keypress == "r"),1,0)

ls.str(df)
```

Create crossmodal correspondence variable
```{r}

df$congruency = ifelse((df$stimcolour %in% "y" & df$Condition == "1")|(df$stimcolour %in% "r" & df$Condition == "2"),1,0) #condition and stimulus is congruent

ls.str(df)
data.frame(df$Condition, df$stimcolour, df$congruency)

```


# Congruency check
```{r}
df$congruency <- as.factor(df$congruency)
df$Condition <- as.factor(df$Condition)
```

```{r}

df %>%
  group_by(congruency) %>%
  summarise(meanrt=mean(ReactionTime))

```

# Eyeballing data
```{r}
hist(df$ReactionTime)
```

```{r}
df %>% ggplot(aes(x = congruency, y = ReactionTime, colour = Condition)) +
  theme_minimal() +
  labs(x = "Congruency", y = "RT",
    title = "RT by congruency")  +
  geom_boxplot(width = 0.5) +
  stat_summary(fun = mean, geom = "point", shape = 23, colour = "Black")
```

```{r}
ggplot(plot_means, aes(x=congruency, y=means, group=Block, color=Block))+
  geom_point()+
  geom_line()+
  geom_errorbar(aes(ymin=means-SEs, ymax=means+SEs), width=.2)+
  theme_classic()+
  ylab("Mean Reaction Time (ms)")+
  xlab("Typing Material")
```

## Analysis 
https://www.crumplab.com/statisticsLab/lab-9-repeated-measures-anova.html

Independent variable: Stimulus, Condition
Dependent: RT, correct

Find mean RT for each condition


## Analysis (Klapetek paper)

- Mean accuracy of participants' responding (expected to be high, above 85% correct)
- Only correct response trials were included in the RT analysis (97% of all trials)
- Should we exclude outliers (were RT falls beyond 2.5 SDs from the participant's mean in a given condition) from the analysis like they did?
- Summarise the mean accuracy rates and RTs for all experimental conditions
- Repeated measures analysis of variance (ANOVA) conducted on the RT data with taste (congruent/incongruent or no taste) as the within-participants factor. Do we find a significant main effects of sound?? 
- Are the RTs similar in the congruent and incongruent conditions?
- Are the RTs substantially longer when no taste is presented?
- Pairwise comparison (TUkey's HSD); does this confirm that the mean RTs differ significantly between no-taste and congruent-taste conditions and between the no-taste and incongruent-taste conditions?
- Is there a significant difference between the congruent and incongruent taste codnitions?

- A second repeated measures ANOVA conducted on the individual participants’ search slopes also revealed a significant main effect of sound

