---
title: "Perception Action Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM")
pacman::p_load(tidyverse,dplyr, data.table, vroom, ggplot2, readbulk, lme4, rstanarm, MuMIn, lmerTest, lme4,multcomp, interactions, sjPlot, sjmisc)
```

Read data
```{r}
df <- read_bulk(directory = "/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/logfiles_emma/",
    fun = read_csv)

#df <- read_csv("/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/logfiles_emma/logfile_test_2021_Dec_13_0937_1.csv")
```

Remove the weird [' '] part of the Colourtask (key press), leaving only the letter
```{r}
df$Colourtask = gsub("'", "", df$Colourtask)
df$Colourtask = gsub("\\[|\\]", "", df$Colourtask)
unique(df$Colourtask)
```

```{r}
df <- df %>% 
  rename(keypress = Colourtask)

```


Making stimulus variable neat (only leaving y1a format)
```{r}

df$Stimulus = gsub("/Users/emmaolsen/OneDrive - Aarhus Universitet/UNI/P&A/Exam/PERC-ACT_EXAM/stimuli/", "", df$Stimulus)
df$Stimulus = gsub(".png", "", df$Stimulus)

```

Make a simple stim variable
```{r}

# df$Stimulus = gsub("a", "", df$Stimulus)
df$Stimulus = gsub("b", "", df$Stimulus)
df$Stimulus = gsub("1234567890", "", df$Stimulus)
length(unique(df$Stimulus))
which(df$Stimulus %in% "y")

```

Do a subset test
```{r}
test <- df %>%
    filter(ID == "sjovtparticipantid")
```


Create correct variable. If variable 'Stimulus' contains character value y, the variable "correct" should be 
```{r}

df$stimcolour <- substr(df$Stimulus,1,1) #just getting the y/r letter out 
df$correct = ifelse((df$stimcolour=="y" & df$keypress == "y") | (df$Stimulus %in% "r" & df$keypress == "r"),1,0)

ls.str(df)
```

Create crossmodal correspondence variable
```{r}

df$congruency = ifelse((df$stimcolour %in% "y" & df$Condition == "1")|(df$stimcolour %in% "r" & df$Condition == "2"),1,0) #condition and stimulus is congruent

ls.str(df)
data.frame(df$Condition, df$stimcolour, df$congruency)

```


# Eyeballing data
```{r}
hist(df$ReactionTime)
```

```{r}
hist(df$Stimulus)
```

## Analysis 
https://www.crumplab.com/statisticsLab/lab-9-repeated-measures-anova.html

Independent variable: Stimulus, Condition
Dependent: RT, correct

Find mean RT for each condition
```{r}
```